%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome} % Add this line to import the fontawesome package
\usepackage{multicol}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

% \begin{center}
%     \textbf{\Huge Matthew Saad} \\ \vspace{1pt}
%     \small (585) 270-9450 $|$ 
%     \href{mailto:msaad02@outlook.com}{\underline{msaad02@outlook.com}} $|$ 
%     \href{https://www.linkedin.com/in/mattsaad/}{\underline{linkedin.com/in/mattsaad}} $|$
%     \href{https://github.com/msaad02}{\underline{github.com/msaad02}}
% \end{center}


\begin{center}
    {\Huge \scshape Matthew Saad} \\ \vspace{3pt}
    \small \raisebox{-0.1\height}{\faPhone}\ 585-270-9450 $|$ 
    \href{mailto:msaad02@outlook.com}{\raisebox{-0.2\height}{\faEnvelope}\  \underline{msaad02@outlook.com}} $|$ 
    \href{https://www.linkedin.com/in/mattsaad/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/mattsaad/}}  $|$
    \href{https://github.com/msaad02}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/msaad02}}
    \vspace{-2pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {SUNY Brockport}{Brockport, NY}
      {B.S. Computer Science/Mathematics}{Aug 2020 -- May 2024}
      \resumeItemListStart
        \resumeItem{Double Major with concentrations in Software Engineering and Statistics.}
        \resumeItem{Honors College; 3.9/4.0 GPA \textit{summa cum laude}.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  % Latest
    \resumeSubheading
    {Excellus BCBS}{Rochester, NY}
    {Business Intelligence Administrator}{Jun 2024 - Present}
    \resumeItemListStart
        \resumeItem{Administered Databricks platform, ensuring secure access control and optimal workspace configurations.}
        \resumeItem{Automated cluster management processes, improving resource efficiency and aligning with security compliance.}
        \resumeItem{Developed SQL-based billing table and built an interactive dashboard to deliver real-time billing insights.}
        \resumeItem{Resolved platform performance and security issues, enhancing the reliability of Databricks and other analytics platforms.}
    \resumeItemListEnd

    % SubSub Heading previous at same company
    \resumeSubSubheading
    {Data Science Intern}{Jun 2022 - May 2024}
    \resumeItemListStart
        \resumeItem{Engineered a KNN and Random Forest-based recommendation engine to enhance member experience.}
        \resumeItem{Led the deployment of a REST API, achieving a 60\% model efficiency gain through refactored code.}
        \resumeItem{Developed three RShiny applications to streamline model scoring and improve operational workflows.}
        \resumeItem{Designed two internal chatbots using generative AI tools, streamlining information dissemination.}
        \resumeItem{Explored the implementation of BERT and T5 models for telehealth call summarization.}
        \resumeItem{Effectively presented work to Excellus BCBS stakeholders, executives, and the broader company.}
    \resumeItemListEnd

    \resumeSubheading
    {SUNY Brockport}{Brockport, NY}
    {Student Employee}{Aug 2022 - May 2024}
    \resumeItemListStart
        \resumeItem{Teaching assistant for CSC203: Object-Oriented Programming and CSC311: Computer Architecture (2 yrs.)}
        \resumeItem{Math tutor in the SUNY Brockport Academic Success Center (1 yr.)}
        \resumeItem{Grader for MTH201: Calculus I (0.5 yr.)}
    \resumeItemListEnd

    \resumeSubheading
    {ActionLink}{Henrietta, NY}
    {Intel Representative}{Sep 2021 - Mar 2023}
    \resumeItemListStart
        \resumeItem{Improved customer engagement with Intel’s initiatives, resulting in increased brand awareness and sales.}
        \resumeItem{Boosted BestBuy Henrietta employee participation in Intel's promotions and programs by 23\%.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{BrockportGPT} $|$ \emph{Senior Honors Thesis} $|$ \href{https://github.com/msaad02/honors-thesis}{\underline{github.com/msaad02/honors-thesis}}}{Apr 2023 -- Jun 2024}
          \resumeItemListStart
            \resumeItem{Leveraged state-of-the-art advancements in generative AI to create a chatbot for SUNY Brockport.}
            \resumeItem{Utilized approaches such as RAG, fine-tuning, and training a from scratch 184M transformer model.}
            \resumeItem{Achieved strong performance that consistently delivers relevant responses to user inquiries.}
            \resumeItem{Presented BrockportGPT at SUNY Brockport Scholars Day, CCSCNE 2024, and SURC 2024.}
          \resumeItemListEnd

        \resumeProjectHeading
            {\textbf{Chess AI Bot} $|$ \emph{AI/ML Final Project} $|$ \href{https://github.com/msaad02/final-project-ai-ml}{\underline{github.com/msaad02/final-project-ai-ml}}}{May 2023}
            \resumeItemListStart
            \resumeItem{Developed a chess AI bot using deep learning techniques with minimax and alpha-beta pruning.}
            \resumeItem{Gained experience with Tensorflow and learned basics of neural network training.}
            \resumeItem{Worked with a team of four to develop and present our final project to the class.}
            \resumeItemListEnd

        \resumeProjectHeading
            {\textbf{Car Price Prediction} $|$ \emph{Data Science Final Project} $|$ \href{https://github.com/msaad02/final-project-data-sci}{\underline{github.com/msaad02/final-project-data-sci}}}{Dec 2021}
            \resumeItemListStart
            \resumeItem{Learned the mathematical foundation behind different machine learning algorithms.}
            \resumeItem{Performed data manipulation on a dataset of used cars to predict their price.}
            \resumeItemListEnd

    \resumeSubHeadingListEnd


%------RELEVANT COURSEWORK-------
% \section{Relevant Coursework}
% \vspace{-15pt}
% %\resumeSubHeadingListStart
%     \begin{multicols}{4}
%         \begin{itemize}[itemsep=-1pt, parsep=3pt]
%             \item\small Artificial Intelligence
%             \item Software Engineering
%             \item Database Management
%             \item Probability Theory
%             \item Data Analytics
%             \item Computer Networks
%             \item Linear Algebra
%             \item Time Series
%         \end{itemize}
%     \end{multicols}
%     \vspace*{2.0\multicolsep}
% %\resumeSubHeadingListEnd
% \vspace{-40pt}


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, R, Java, SQL, C, Bash} \\
     \textbf{Developer Tools}{: Azure, AWS, Databricks, Git, Docker, HuggingFace, Posit Connect} \\
     \textbf{Libraries}{: PyTorch, Tensorflow, Tidyverse, pandas, NumPy, Matplotlib}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
